QPLIB: A Library of Quadratic Programming Instances

### 2018-02-02 AnswerToTheReferees.tex

\item Page 17. Doesn't CPLEX support some binary non-convex quadratic
problems.

\rep{ TODO:Fabio and Emiliano
%\leo{rispondiamo al referee che CPLEX e` classificato 'C' (complete) in tavola 2 rispetto a QGC e ricordiamogli che pero` CPLEX non risolve (a mia conoscenza e per il momento) QGQ. Tra l'altro, c'e` a p. 17 una menzione di "Table 2 below", tranne che la table 2 appare above. Diciamo solo "Table 2" senza il below e l'above, dato che la posizione di tavole e figure puo` comunque essere modificata sia da LaTeX sia dal typesetting finale.} 
}

\item Page 19. I think it would be interesting to give a bit more details about the conic constraints and relate it with the issue of what is a convex
constraint I discuss in point 2. I think the argument is that problems with
non-convex quadratic constraints (i.e. $f (x) \le 0$ with $f$ non-convex) may
have a convex feasible region. I imagine that detecting this in general may
be NP-hard even though the conic case (1 negative eigenvalue) is relatively
easy (e.g. if the problem includes an inequality of the form $a \cdot x \ge$ where
a is the eigenvector associated to the negative eigenvalue). It would then
be interesting to mark the problems with non-convex constraints, but for
which it is known how to show the convexity of the complete feasible
region (because they are conic or another ad-hoc reason).

\rep{We thank the referee for bringing up this point. We addressed it in two comments in Sections 2.2.1 and 2.2.2. 
%TODO: Leo
% \leo{sono d'accordo col referee (ovvero: massi`, facciamolo contento)} \fabio{va qui? o e' un commento al punto di sotto?}
 }

@@

can be solved to global optimality as long as the matrix is second-order sufficient. This means
that even some QPs with indefinite Hessians can easily be solved to global optimality.

\rep{Thank you for having raised this point. We addressed in Sections 2.2.1 and 2.2.2.
%TODO:Antonio. 
%lo dicevamo già a p. 10, ma grazie per avercelo ricordato: adesso lo richiamiamo brevemente in §2.2.1 e lo discutiamo in §2.2.2
%
%\leo{cosa vuol dire? Questa condizione si puo` testare in polytime? Sicuramente puo` entrare nel discorso a risposta dei punti 2-4 del referee \#1.} 
}

\item The discussion on p.9 recounts some textbook facts, and is largely superfluous. Delete it.

\rep{
Although all the facts recalled in \S 2.2.2 are in fact well known, we still feel they need to be discussed in this context because they illustrate how the taxonomy (as almost all of them) has some grey areas whereby the same underlying problem can be described by instances that would be classified differently. This is, as the header of the section recalls, strongly tied to the concept of reformulation. One relevant example is the relationship between definiteness of the Hessians and convexity, correctly pointed out by the referee, which is naturally discussed in \S 2.2.2. One of the nontrivial choices in our library is that we made no effort to reformulate the instances (although of course we could have), and inserted them in the library in the very same format they have been provided to us by the original contributors. Section 2.2.2 is crucial in justifying this choice, as it shows that there are several degrees of freedom to move the instances from one class to another. Doing so, however, is typically justified by the fact that this makes one specific solver more efficient in solving them, a bias that we don't want to add. Hence, we have chosen to keep the instances in their ``natural'' format, this being the one in which the original contributor initially wrote them.
%TODO: Antonio.
%\leo{cancelliamo tutto!} 
%As requested, aliminated the discussion from the manuscript
}

### 2018-02-02 QPLIB-2.2.tex
Update QPLIB-2.2.tex

Our taxonomy is based on a three-fields code of the form ``\textit{OVC}'', where \textit{O} indicates the type of objective function considered, \textit{V} records the types of variables, and \textit{C} designates the types of constraints imposed on the variables. The fields can be given the following values:
%
\begin{itemize}
 \item objective function: (\textit{L})inear, (\textit{D})iagonal convex (if minimization) or concave (if maximization) quadratic, (\textit{C})onvex (if minimization) or (\textit{C})oncave (if maximization) quadratic,  (\textit{Q})uadratic (all other cases);
 %
 \item variables: (\textit{C})ontinuous only, (\textit{B})inary only, (\textit{M})ixed binary and continuous, (\textit{I})nteger (including binary) only, (\textit{G})eneral (all other cases);
 %
 \item constraints: (\textit{N})one, (\textit{B})ox, (\textit{L})inear, (\textit{D})iagonal convex quadratic, (\textit{C})on\-vex quadratic, nonconvex (\textit{Q})uadratic.
  Note that (\textit{D}) and (\textit{C}) are intended to mean that the feasible set of the constraint is convex, i.e., that either $Q^i$ is positive semidefinite and $c_l^i = -\infty$, or $Q^i$ is negative semidefinite and $c_u^i = \infty$. 
    \textcolor{red}{Note that (positive or negative) definiteness of $Q^i$ is a sufficient, but not in general necessary, condition for convexity. As detailed in \S\ref{subsec:final set}, in our taxonomy we mark the constraints ``$C$'' based on the sufficient condition alone, the rationale of this choice being discussed in \S\ref{ssec:reform}.}
  Quadratic constraints with both finite bounds cannot ever be convex (unless $Q^i = 0$, i.e., they are not ``truly'' quadratic constraints).
\end{itemize}
%
The wildcard ``*'' will be used below to indicate any possible choice, and lists of the form ``\{\textit{X}, \textit{Y}, \textit{Z}\}'' will indicate that the value of the given field can freely attain any of the specified values.

>>>>

Our taxonomy is based on a three-fields code of the form ``\textit{OVC}'', where \textit{O} indicates the type of objective function considered, \textit{V} records the types of variables, and \textit{C} designates the types of constraints imposed on the variables. The fields can be given the following values:
%
\begin{itemize}
 \item objective function: (\textit{L})inear, (\textit{D})iagonal convex (if minimization) or concave (if maximization) quadratic, (\textit{C})onvex (if minimization) or (\textit{C})oncave (if maximization) quadratic,  (\textit{Q})uadratic (all other cases);
 %
 \item variables: (\textit{C})ontinuous only, (\textit{B})inary only, (\textit{M})ixed binary and continuous, (\textit{I})nteger (including binary) only, (\textit{G})eneral (all other cases);
 %
 \item constraints: (\textit{N})one, (\textit{B})ox, (\textit{L})inear, (\textit{D})iagonal convex quadratic, (\textit{C})on\-vex quadratic, nonconvex (\textit{Q})uadratic.
  Note that (\textit{D}) and (\textit{C}) are intended to mean that either $Q^i$ is positive semidefinite and $c_l^i = -\infty$, or $Q^i$ is negative semidefinite and $c_u^i = \infty$. 
    \textcolor{red}{Note that (positive or negative) definiteness of $Q^i$ is a sufficient, but not in general necessary, condition for convexity. As detailed in \S\ref{subsec:final set}, in our taxonomy we mark the constraints ``$C$'' based on the sufficient condition alone, the rationale of this choice being discussed in \S\ref{ssec:reform}.}
  Quadratic constraints with both finite bounds cannot ever be convex (unless $Q^i = 0$, i.e., they are not ``truly'' quadratic constraints).
\end{itemize}
%
The wildcard ``*'' will be used below to indicate any possible choice, and lists of the form ``\{\textit{X}, \textit{Y}, \textit{Z}\}'' will indicate that the value of the given field can freely attain any of the specified values.
